Growth model analysis

### 2018-01-30 manuscriptAnalysis/MS_Analysis.Rmd
all 3 species models running

```{r}
library(tidyverse)
d <- dddG[[1]]
load("D:/projects/linkedModels/data/out/ddD_bktbntats_1997.RData")
load("D:/projects/linkedModels/data/out/countsAndMasses.RData")
```

@@

>>>>

```{r}
library(arrayhelpers)
library(tidyverse)

load("D:/projects/linkedModels/data/out/ddD_bktbntats_1997.RData")
load("D:/projects/linkedModels/data/out/countsAndMasses.RData")

mcmc <- list()
load("D:/projects/linkedModels/data/out/dG_1517338587_bkt1997_Nimble.RData")
mcmc[['bkt']] <- mcmcProcessed
d <- dddG[[1]]

load("D:/projects/linkedModels/data/out/dG_1517344974_bnt1997_Nimble.RData")
mcmc[['bnt']]  <- mcmcProcessed

load("D:/projects/linkedModels/data/out/dG_1517347750_ats1997_Nimble.RData")
mcmc[['ats']]  <- mcmcProcessed

rm(dddG,ddG,dG,mcmcProcessed)
```

@@

```{r mcmc output analysis}

riverOrderedIn <- factor(c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),levels=c('west brook', 'wb jimmy', 'wb mitchell',"wb obear"),labels = c("west brook","wb jimmy","wb mitchell","wb obear"), ordered = T)

grInt <- list()
grInt[['bkt']] <- array2df(mcmc[['bkt']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int")
grInt[['bnt']] <- array2df(mcmc[['bnt']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="int")
grInt[['ats']] <- array2df(mcmc[['ats']]$sims.list$grInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="int")

ggplot( grInt[['bkt']] %>% filter(river %in% c('west brook','wb jimmy')), aes(int)) +
  geom_freqpoly(binwidth=0.05) +
  geom_freqpoly(aes(int),color = 'brown', data = grInt[['bnt']]) +
  geom_freqpoly(aes(int),color = 'lightblue', data = grInt[['ats']]) +
  xlim(-0.5,1.5) +
  theme_publication() +
  facet_grid(season ~ river + isYOY)

sigmaInt <- list()
sigmaInt[['bkt']] <- array2df(mcmc[['bkt']]$sims.list$sigmaInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:4]), label.x="int")
sigmaInt[['bnt']] <- array2df(mcmc[['bnt']]$sims.list$sigmaInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:2]), label.x="int")
sigmaInt[['ats']] <- array2df(mcmc[['ats']]$sims.list$sigmaInt, levels = list(iter=NA,isYOY=c(0,1),season=1:4,river=riverOrderedIn[1:1]), label.x="int")

ggplot( sigmaInt[['bkt']] %>% filter(river %in% c('west brook','wb jimmy')), aes(int)) +
  geom_freqpoly() +
  geom_freqpoly(aes(int),color = 'brown', data = sigmaInt[['bnt']]) +
  geom_freqpoly(aes(int),color = 'lightblue', data = sigmaInt[['ats']]) +
  xlim(-4.5,-1) +
  theme_publication() +
  facet_grid(season ~ river + isYOY)

```
```{r ind RE among spp}

grIndRE <- list()
grIndRE[['bkt']] <- as.data.frame(mcmc[['bkt']]$q50$grIndRE); names(grIndRE[['bkt']]) <- 'value'
grIndRE[['bnt']] <- as.data.frame(mcmc[['bnt']]$q50$grIndRE); names(grIndRE[['bnt']]) <- 'value'
grIndRE[['ats']] <- as.data.frame(mcmc[['ats']]$q50$grIndRE); names(grIndRE[['ats']]) <- 'value'

ggplot( grIndRE[[1]], aes(value) ) +
  geom_freqpoly(binwidth = 0.0025) +
  geom_freqpoly(aes(value), color = "brown", binwidth = 0.0025, data = grIndRE[[2]]) +
  geom_freqpoly(aes(value), color = "lightblue", binwidth = 0.0025, data = grIndRE[[3]])
